An effective and friendly tool for seed image analysis

### 2021-03-31 main.tex
fix images, added affiliations, uploaded to arxiv

\title{An effective and friendly tool for seed image analysis}
\author{Andrea, Alessandra, Mariano, Cecilia, Bacchetta}
%\date{date ../../....}

@@

\begin{figure}[tbp]
	\centerline{\includegraphics[scale=0.5]{Img/Sardinia.png}}
	\caption{Examples of seeds images present in the \emph{Fabaceae} dataset.}
	\label{Sardinia}
\end{figure}

@@

\begin{figure}[!t]
	\centerline{\includegraphics[scale=0.37]{Img/Fig1.eps}}
	\caption{ImageJ main interface.}
	\label{ImageJ_Interf}
\end{figure}
Basic operations, like file opening or simple editing options (File and Edit options) and more complex ones, such as segmentation operations, image enhancement, noise reduction, object counting, filtering, and other options ("Image," "Process," "Analyze" and "Plugins"), are accessible from the main menu.
Moreover, the toolbar contains several options to select regions or shapes in the image. 
The status bar shows the current pixel's coordinates and values when the cursor is over the image. Simultaneously, whether a filter operation is performed on the image, the status bar displays the execution time and the processing speed in $pixels / second$.
The progress bar, shown on the right-hand side of the status bar, shows the processing progress.

@@

\subsection{A plugin for feature extraction from seeds image}
\label{seeds_analyser}
\emph{SeedsAnalyser} is the plugin for feature extraction proposed in this work and needs a minimal number of user interactions. It aims to identify and analyse multiple seeds represented in a digital image. The input is a single image acquired with a quasi-uniform blue background.
The plugin is also able to analyse all the images in a specific folder at the same time. Each image can present a blue background in a wide range of tones, varying from a very light blue to a very dark navy blue. After the acquisition, the image is preprocessed for the correct separation of the regions of interest, namely the single seeds. 
It is possible to isolate the Blue value of the RGB images to get pure masks as the dataset backgrounds are all in various shades of blue (see Figure \ref{Sardinia_Masks}), as indicated in our previous work \cite{Loddo20}. 
Creating a single seed dataset from the original database is possible thanks to different backgrounds of various blue shades. It allowed finding the best images to work on and making the binary masks to extract the single seeds just by an automatic thresholding procedure.
During the acquisition, the seeds were well spaced from each other. Therefore the bounding box of each region allowed the creation of a single seed image for analysis quickly.
From the \emph{Fabaceae} dataset, we selected the images containing the most numerous samples per species for 23 different species and nearly 2000 seeds.
We discarded some species due to the low sharpness and too small size of the seeds. Figures \ref{Sardinia_Masks} and \ref{Sardinia_Crops} show an original sample image with its derived binary mask and some seed images extracted from it, respectively. 
\begin{figure}[tbp]
	\centering
	\includegraphics[scale=0.6]{Img/SardiniaMasks.png}
	\caption{Example of an image from the \emph{Fabaceae} database and its derived binary mask.}
	\label{Sardinia_Masks}
\end{figure}

\begin{figure}[tbp]
	\centering
	\includegraphics[scale=0.4]{Img/Sardinia_crops.png}
	\caption{Some examples of seed images extracted from the image of Figure \ref{Sardinia_Masks} of the \emph{Fabaceae} database.}
	\label{Sardinia_Crops}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[height=0.35\textheight]{Img/f3_features_selection.png}
\caption{\label{fig:features_selection}Window for feature selection.}
\end{figure}

>>>>

\title{An effective and friendly tool for seed image analysis}

%% Group authors per affiliation:
\author[1]{Loddo A. \footnote{Corresponding author: Andrea Loddo (andrea.loddo@unica.it)} }
\author[1]{Di Ruberto C.}
\author[2]{Vale A.M.P.G.}
\author[3]{Ucchesu M.}
\author[4]{Soares J.M.}
\author[3,5]{Bacchetta G.}

\affil[1]{Department of Mathematics and Computer Science, University of Cagliari, via Ospedale 72, 09124 Cagliari.}
\affil[2]{Escola Agrícola de Jundiaí (EAJ), Universidade Federal do Rio Grande do Norte (UFRN), Rodovia RN 160, Km 03, CEP 59280-000 Macaíba (RN), Brasil.}
\affil[3]{Centro Conservazione Biodiversità (CCB), Dipartimento di Scienze della Vita e dell’Ambiente (DiSVA), Università degli Studi di Cagliari, Viale S. Ignazio da Laconi 13, 09123 Cagliari, Italy.}
\affil[4]{Universidade Federal do Rio Grande do Norte (UFRN), Rodovia RN 160, Km 03, CEP 59280-000 Macaíba (RN), Brasil.}
\affil[5]{Hortus Botanicus Karalitanus (HBK), Università degli Studi di Cagliari, Viale S. Ignazio da Laconi 11, 09123 Cagliari, Italy.}

%\fntext[myfootnote]{}

@@

\begin{figure}[tbp]
	\centerline{\includegraphics[scale=0.5]{Img/Sardinia.jpg}}
	\caption{Examples of seeds images present in the \emph{Fabaceae} dataset.}
	\label{Sardinia}
\end{figure}

@@

\begin{figure}[!t]
	\centerline{\includegraphics[scale=0.37]{Img/Fig1.pdf}}
	\caption{ImageJ main interface.}
	\label{ImageJ_Interf}
\end{figure}
Basic operations, like file opening or simple editing options (File and Edit options) and more complex ones, such as segmentation operations, image enhancement, noise reduction, object counting, filtering, and other options ("Image," "Process," "Analyze" and "Plugins"), are accessible from the main menu.
Moreover, the toolbar contains several options to select regions or shapes in the image. 
The status bar shows the current pixel's coordinates and values when the cursor is over the image. Simultaneously, whether a filter operation is performed on the image, the status bar displays the execution time and the processing speed in $pixels / second$.
The progress bar, shown on the right-hand side of the status bar, shows the processing progress.

@@

\subsection{A plugin for feature extraction from seeds image}
\label{seeds_analyser}
\emph{SeedsAnalyser} is the plugin for feature extraction proposed in this work and needs a minimal number of user interactions. It aims to identify and analyse multiple seeds represented in a digital image. The input is a single image acquired with a quasi-uniform blue background.
The plugin is also able to analyse all the images in a specific folder at the same time. Each image can present a blue background in a wide range of tones, varying from a very light blue to a very dark navy blue. After the acquisition, the image is preprocessed for the correct separation of the regions of interest, namely the single seeds. 
It is possible to isolate the Blue value of the RGB images to get pure masks as the dataset backgrounds are all in various shades of blue (see Figure \ref{Sardinia_Masks}), as indicated in our previous work \cite{Loddo20}. 
Creating a single seed dataset from the original database is possible thanks to different backgrounds of various blue shades. It allowed finding the best images to work on and making the binary masks to extract the single seeds just by an automatic thresholding procedure.
During the acquisition, the seeds were well spaced from each other. Therefore the bounding box of each region allowed the creation of a single seed image for analysis quickly.
From the \emph{Fabaceae} dataset, we selected the images containing the most numerous samples per species for 23 different species and nearly 2000 seeds.
We discarded some species due to the low sharpness and too small size of the seeds. Figures \ref{Sardinia_Masks} and \ref{Sardinia_Crops} show an original sample image with its derived binary mask and some seed images extracted from it, respectively. 
\begin{figure}[tbp]
	\centering
	\includegraphics[scale=0.6]{Img/SardiniaMasks.jpg}
	\caption{Example of an image from the \emph{Fabaceae} database and its derived binary mask.}
	\label{Sardinia_Masks}
\end{figure}

\begin{figure}[tbp]
	\centering
	\includegraphics[scale=0.4]{Img/Sardinia_crops.jpg}
	\caption{Some examples of seed images extracted from the image of Figure \ref{Sardinia_Masks} of the \emph{Fabaceae} database.}
	\label{Sardinia_Crops}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[height=0.35\textheight]{Img/f3_features_selection.jpg}
\caption{\label{fig:features_selection}Window for feature selection.}
\end{figure}
